ANGSD-wrapper: utilities for analyzing next generation sequencing data

### 2016-01-20 manuscript.tex
fix parv spelling

Finally, we include two samples of the related wild teosinte \textit{Zea mays} ssp. {mexicana} to assess evidence for admixture.  
Using the Admixture method, which implements an estimate of admixture proportion from genotype likelihoods \citep{pmid24026093}, we identify  structure within domesticated maize separating three high-latitude temperate landraces from the other tropical accessions (Figure \ref{fig:admixture}).\jri{parviglumis spelled wrong in figure legend}
We find no evidence of admixture between these lowland maize samples and  ssp. {mexicana}, consistent with an independent analysis from SNP genotyping \citep{hufford2013genomic}.
\textit{Zea mays} ssp. {mexicana} clusters into its own group, along with a single accession of ssp. {parviglumis} collected from region in which many teosinte populations appear to be the result of admixture between the two subspecies \citep{fang2012megabase}.  
A single  ssp. {parviglumis} accession from the Northern extent of the range does not appear to be well-classified with these data, likely due to our relatively limited geographic and genomic sampling.

>>>>

Finally, we include two samples of the related wild teosinte \textit{Zea mays} ssp. {mexicana} to assess evidence for admixture.  
Using the Admixture method, which implements an estimate of admixture proportion from genotype likelihoods \citep{pmid24026093}, we identify  structure within domesticated maize separating three high-latitude temperate landraces from the other tropical accessions (Figure \ref{fig:admixture}).
We find no evidence of admixture between these lowland maize samples and  ssp. {mexicana}, consistent with an independent analysis from SNP genotyping \citep{hufford2013genomic}.
\textit{Zea mays} ssp. {mexicana} clusters into its own group, along with a single accession of ssp. {parviglumis} collected from region in which many teosinte populations appear to be the result of admixture between the two subspecies \citep{fang2012megabase}.  
A single  ssp. {parviglumis} accession from the Northern extent of the range does not appear to be well-classified with these data, likely due to our relatively limited geographic and genomic sampling.
